Internal models of type theory and internal higher categories for the Univalent Foundations

### 2014-05-16 article-models-ttderived.tex
stated and proved a fundamental lemma for wkalg-exteq2
changed a word

\begin{lem}\label{lem:jcomp-const}
The inference
\begin{align*}
& \inference
  { \jhom{\Gamma}{A}{B}{f}
    \jhom{\Gamma}{B}{C}{g}
    \jfam{{\Gamma}{A}}{P}
    }
  { \jhomeq
      {\Gamma}
      {{A}{P}}
      {C}
      {\ctxwk{P}{\jcomp{A}{f}{g}}}
      {\jcomp{{A}{P}}{\ctxwk{P}{f}}{g}}
    }
\end{align*}
tells what happens when we weaken a composition, which is a term of 
$\ctxwk{A}{C}$, by a family $P$ over $\ctxext{\Gamma}{P}$. We also have the following
inference rules expressing that compositions by or with constant morphisms are
again constant morphisms.
\begin{align*}
& \inference
  { \jterm{\Gamma}{B}{y}
    \jhom{\Gamma}{B}{C}{g}
    }
  { \jhomeq
      {\Gamma}
      {A}
      {C}
      {\jcomp{A}{\ctxwk{A}{y}}{g}}
      {\ctxwk{A}{\subst{y}{g}}}
    }
  \\
& \inference
  { \jhom{\Gamma}{A}{B}{f}
    \jterm{\Gamma}{C}{z}
    }
  { \jhomeq
      {\Gamma}
      {A}
      {C}
      {\jcomp{A}{f}{\ctxwk{B}{z}}}
      {\ctxwk{A}{z}}
    }
\end{align*}
\end{lem}

@@

We end this subsection with a simple application of the above lemmas that is
typical for the more general formulation of composition we have
introduced. It is a special case of a consecutive composition where we consider
a morphism $\jhom{\Gamma}{A}{B}{f}$ and a morphism
$\jhom{{{\Gamma}{B}}{Q}}{R}{S}{g}$.

>>>>

\begin{lem}\label{lem:jcomp-const}
The inference rule
\begin{align*}
& \inference
  { \jhom{\Gamma}{A}{B}{f}
    \jhom{\Gamma}{B}{C}{g}
    \jfam{{\Gamma}{A}}{P}
    }
  { \jhomeq
      {\Gamma}
      {{A}{P}}
      {C}
      {\ctxwk{P}{\jcomp{A}{f}{g}}}
      {\jcomp{{A}{P}}{\ctxwk{P}{f}}{g}}
    }
\end{align*}
tells what happens when we weaken a composition, which is a term of 
$\ctxwk{A}{C}$, by a family $P$ over $\ctxext{\Gamma}{P}$. We also have the following
inference rules expressing that compositions by or with constant morphisms are
again constant morphisms.
\begin{align*}
& \inference
  { \jterm{\Gamma}{B}{y}
    \jhom{\Gamma}{B}{C}{g}
    }
  { \jhomeq
      {\Gamma}
      {A}
      {C}
      {\jcomp{A}{\ctxwk{A}{y}}{g}}
      {\ctxwk{A}{\subst{y}{g}}}
    }
  \\
& \inference
  { \jhom{\Gamma}{A}{B}{f}
    \jterm{\Gamma}{C}{z}
    }
  { \jhomeq
      {\Gamma}
      {A}
      {C}
      {\jcomp{A}{f}{\ctxwk{B}{z}}}
      {\ctxwk{A}{z}}
    }
\end{align*}
\end{lem}

@@

We end this subsection with a simple application of the above lemmas that is
illustrative for the more general formulation of composition we have
introduced. It is a special case of a consecutive composition where we consider
a morphism $\jhom{\Gamma}{A}{B}{f}$ and a morphism
$\jhom{{{\Gamma}{B}}{Q}}{R}{S}{g}$.
